---
title: "Skills test"
author: "Cody Iordachescu"
date: "11/17/2020"
output: html_document
---

```{r,echo=FALSE,include=FALSE}
library(tidyverse)
library(ggpubr)
library(plotly)
library(broom)
```

## Task 1



### Quick look at the dataframe we are working with 
```{r setup,include=TRUE,echo=TRUE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE)

df <- read_csv("./FacultySalaries_1995.csv")
head(df)
```

#### First thing to do is convert it to long format:
```{r}
dflong <- df%>% pivot_longer(cols = c("AvgFullProfSalary","AvgAssocProfSalary","AvgAssistProfSalary"),
                             names_to = "Rank",
                             values_to= "Salary",names_prefix="Avg")
head(dflong)

```

### Next, some clean up and reclassing:

```{r, eval=TRUE}
#Adjust ranks to match graph
dflong$Rank <- str_remove(dflong$Rank,pattern = "ProfSalary")
  #need to change some column classes
dflong$Rank <- as.factor(dflong$Rank)
#test out the plot
ggplot(dflong,aes(x=Tier,y=Salary,fill=Rank))+geom_boxplot()
#looks like there is an incorrect tier. Considering the levels of the Tier column and the frequency of VIIB, I will just have it removed 
dflong <- dflong[-(which(dflong$Tier=="VIIB")),]

```

### Finally our recreated plot:

```{r,fig.height=11,fig.width=9.35}
#let's retest the plot
ggplot(dflong,aes(x=Rank,y=Salary,fill=Rank))+geom_boxplot()+theme_minimal()+facet_wrap(~Tier)+theme(axis.text.x = element_text(angle=60))
```
___

## Task 2

### Making an anova table of the data from task 1


```{r}
mod1 <- glm(data = dflong,formula = Salary~State+Tier+Rank,method = "glm.fit")
summary(aov(mod1))
```

### That was easy.

## Task 3

### Clean up a new data set by collapsing colunms of chemical concentrations into rows of compound names and concentrations:

```{r}
#read the data
df1 <- read_csv(file = "./Juniper_Oils.csv")
#Woah, Right off the bat I will combine the oils into two columns. Thanks for the chem names!!

df1long<- df1%>%pivot_longer(cols = c("alpha-pinene","para-cymene","alpha-terpineol","cedr-9-ene","alpha-cedrene","beta-cedrene","cis-thujopsene","alpha-himachalene","beta-chamigrene","cuparene","compound 1","alpha-chamigrene","widdrol","cedrol","beta-acorenol","alpha-acorenol","gamma-eudesmol","beta-eudesmol","alpha-eudesmol","cedr-8-en-13-ol","cedr-8-en-15-ol","compound 2","thujopsenal"),
                             names_to="Oil_type",values_to= "Concentration")
```


## Task 4

### Use the cleaned up data to create a new plot:

```{r}
#Task IV####
library(broom)
ggplot(df1long,aes(x=YearsSinceBurn,y=Concentration))+
  geom_point()+
  geom_smooth()+
  facet_wrap(~Oil_type,scales = "free_y")
```

## Task 5

### This code identifies chemicals that have a significantly(Pval=0.05) different concentration as a function of time since the plant died.

```{r}

#Task V
modtree <- glm(formula = Concentration~Oil_type*YearsSinceBurn,data = df1long)
results_df <- summary(modtree)$coefficients
results_df%>%as.data.frame(colnames=TRUE)%>%filter(`Pr(>|t|)`<=.05)
```

## Task 6 

### Push all of these files to github.

## Task 7

### Make this markdown document. Done. Sweet!

